Tropopause Evolution in a Rapidly Intensifying Tropical Cyclone: A Static Stability Budget Analysis

### 2017-11-27 paper.tex
Added Model Setup section, along with a number of citations

>>>>

The numerical simulations were performed using version 19.4 of Cloud Model 1 (CM1) described in \cite{BryanRotunno2009} and available online at http://www2.mmm.ucar.edu/people/bryan/cm1/.
The fully-compressible equations of motion were integrated on a 3000-km-wide, 35-km-deep, axisymmetric grid with 1-km horizontal and 250-m vertical grid spacing.
Horizontal turbulence was parameterized using a Smagorinsky scheme described in \citeauthor{BryanRotunno2009} (\citeyear{BryanRotunno2009}, their Eq. 17), with a prescribed mixing length that varied linearly from 100 m at a surface pressure of 1015 hPa to 1000 m at a surface pressure of 900 hPa.
This formulation allows for realistically-large horizontal mixing lengths near the hurricane's inner core, consistent with the results of \cite{Bryan2012}, while not over-representing horizontal turbulence in convection at outer radii.
Vertical turbulence was parameterized using the formulation of \citeauthor{MarkowskiBryan2016} (\citeyear{MarkowskiBryan2016}, their Eq. 6), using an asymptotic vertical mixing length of 100 m.
A Rayleigh damping layer was applied outside of the 2900-km radius and above the 25-km level to prevent spurious gravity wave reflection at the model boundaries.
Microphysical processes were parameterized using the \cite{Thompson} microphysics scheme and radiative heating tendencies were computed every two minutes using the RRTMG longwave and shortwave schemes \citep{Iacono}.
A horizontally-homogeneous temperature and humidity field was initialized with a mean sounding computed using all dropsondes deployed during the TCI flight conducted within and around Tropical Storm Patricia on 21 October, 2015 (see \citeauthor{DoyleTCI} \citeyear{DoyleTCI} for details.)
Above 19 km, where few TCI observations were available, the temperature profile was assumed to be isothermal.
Since relative humidity measurements were unreliable at temperatures below -40\textdegree C \citep{BellTCI}, the water vapor mixing ratio was set to zero above 16 km.
